### 2019-10-21 MAC_publications/2018_nips_vigil/introduction.tex
Move MAC publications files into subdir

Several VQA datasets have been proposed (e.g. DAQUAR~\cite{malinowski2014multi}, VQA~\cite{antol2015vqa}); nonetheless, these datasets contain several biases (e.g. unbalanced questions or answers) that are often exploited by systems during learning~\cite{goyal2017making}.
The CLEVR dataset~\cite{johnson2017clevr} was designed to address these issues. The synthetic nature of its images \& questions enables detailed analysis of visual reasoning, and allows for variations, to test a particular ability such as generalization or transfer learning. One variation of CLEVR, called CoGenT (Compositional Generalization Test), measures whether models learn separate representations for color and shape instead of memorizing all possible combinations.

One of the most recent exciting models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\cite{hudson2018compositional}, which performs a sequence of attention-based reasoning operations. 
though the performance of MAC has been proven, several questions arise:
Does the model really learn relations between objects? 
How does the model represent these relations in its reasoning steps? 
Is the model representing concepts like objects attributes (shape, color, size)?

@@

The paper is organized as follows.
In \sec{datasets} we delve into details of both CLEVR and CoGenT datasets, emphasizing their differences.
Next, in \sec{models} we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
\sec{experiments} discusses the most important results of using transfer learning 
on CLEVR and on both versions of CoGenT.
\sec{transfer_learning} focuses on a cherry-picked subset of experiments to highlight our findings; 
see~Appendix~\ref{sec:full_comparison} for the complete set of results comparing MAC and S-MAC models when training/fine-tuning/testing on various datasets.
In \sec{failures} we show examples supporting hypothesis on the lack of disentanglement of concepts in both models.
\sec{comparison} presents results obtained by other state-of-the-art models, and discusses the challenges faced  
with their reproducibility. 
\sec{conclusion} concludes the paper.

>>>>

Several VQA datasets have been proposed (e.g. DAQUAR~\cite{malinowski2014multi}, VQA~\cite{antol2015vqa}); nonetheless, these datasets contain several biases (e.g. unbalanced questions or answers) that are often exploited by systems during learning~\cite{goyal2017making}.
The CLEVR dataset~\cite{johnson2017clevr} was designed to address these issues. The synthetic nature of its images \& questions enables detailed analysis of visual reasoning, and allows for variations, to test a particular ability such as generalization or transfer learning. One variation of CLEVR, called CoGenT (Compositional Generalization Test), measures whether models learn separate representations for color and shape instead of memorizing all possible combinations. 
For details, see Appendix~A (all appendices are in the supplementary material).

One of the most recent exciting models aiming at solving VQA is called Memory, Attention, and Composition (MAC)~\cite{hudson2018compositional}, which performs a sequence of attention-based reasoning operations. 
Although the performance of MAC has been proven, several questions arise:
Does the model really learn relations between objects? 
How does the model represent these relations in its reasoning steps? 
Is the model representing concepts like objects attributes (shape, color, size)?

@@

### 2019-10-21 MAC_publications/2018_nips_vigil/mac.tex
Move MAC publications files into subdir

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs sequential reasoning, where each step involves analyzing a part of the question followed by shifting the attention over the image.
The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
The input unit  uses an LSTM~\cite{hochreiter1997long} to process the question in a word-by-word manner producing a sequence of \emph{contextual words} and a final \emph{question representation}.
Besides, the input unit utilizes a pre-trained ResNet~\cite{he2016resnet} followed by two CNN layers to extract a feature map (referred to as \emph{knowledge base}) from the image.

>>>>

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs sequential reasoning, where each step involves analyzing a part of the question followed by shifting the attention over the image.
The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
The input unit  uses an LSTM~\cite{hochreiter1997long} to process the question in a word-by-word manner producing a sequence of \emph{contextual words} and a final \emph{question representation}.
Additionally, the input unit uses a pre-trained ResNet~\cite{he2016resnet} followed by two CNN layers to extract a feature map (referred to as \emph{knowledge base}) from the image.

### 2019-10-21 MAC_publications/2018_nips_vigil/smac.tex
Move MAC publications files into subdir

@@

\noindent\textit{Notation.}
%Let $q$ denote the global context of the question
%and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
For each knowledge base $\kb$, a tensor of dimension $H \times W \times d$, let $\kb_{hw}$ be the $d$-dimensional vector indexed by 
$h \in \{1,2,\dots,H\}$ and $w \in \{1,2,\dots, W\}$.
Let $i$ denote the index (position) $i$ of the reasoning step.

@@

\newpage

\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
	           & \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	{\color{Plum}
	\begin{align*}
	&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
	&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} \rr_i + b_{rm}^{[d]} \tag{w1}
	\end{align*}}
\end{multicols}

>>>>

\noindent\textit{Notation.}
%Let $q$ denote the global context of the question
%and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
For each knowledge base $\kb$ of dimension $H \times W \times d$, let $\kb_{hw}$ be the $d$-dimensional vector indexed by 
$h \in \{1,2,\dots,H\}$ and $w \in \{1,2,\dots, W\}$.
Let $i$ denote the index (position) $i$ of the reasoning step.

@@

@@

\vskip -0.6cm

\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
	           & \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	{\color{Plum}
	\begin{align*}
	&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
	&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
	\end{align*}}
\end{multicols}

### 2019-10-21 MAC_publications/2018_nips_vigil_poster/main.tex
Move MAC publications files into subdir

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Contributions}{name=contributions,column=0,row=0}{
\begin{itemize}
	\compresslist
	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model~\cite{hudson2018compositional}, which achieves comparable accuracy while training \emph{\textbf{faster}}.
	\item[$\bullet$] We evaluate the MAC model and the simplified variant on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a \emph{\textbf{15 point increase}} in accuracy, matching the state of the art.
	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can \emph{\textbf{reduce a model's accuracy}}.

@@

\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=mac-model, column=0, below=contributions}{
	\vspace{-10pt}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.33\textwidth]{../img/mac_cell.pdf}
		\caption{The MAC cell, based on~\cite{hudson2018compositional}.}
		\label{fig:mac_cell}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
		\compresslist
		\item[$\bullet$] MAC network: a recurrent model performing sequential reasoning. At each step, it analyzes the question and shifts the attention over the image.
		\item[$\bullet$] Recurrent MAC cell: consists of a control unit, a read unit \& a write unit. The control unit updates the control state $c_i$ \& drives the attention over the question words.
		\item[$\bullet$] The read unit, guided by $c_i$ extracts information from the image. The write unit uses this information to update the memory state $m_i$.
	\end{itemize}
}

\headerbox{Simplified MAC Model (S-MAC)}{name=s-mac, column=0, below=mac-model}{

@@

	\begin{itemize}
		\compresslist
	    \item[$\bullet$] Taking the MAC cell equations as a whole, consecutive linear layers (with no non-linear activation in-between) can be combined as one linear layer.
		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss.
    \end{itemize}

	This allows, with a careful reorganization, to apply a single linear layer to the \textit{knowledge base} (feature map extracted from the image) prior to all the reasoning steps and work with this projection throughout the reasoning steps.\\

@@

\vspace{-15pt}
\begin{table}[H]
	\centering
	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
	\begin{tabular}{llll}
		\toprule
		Model        & Read Unit               & Write Unit &  Control Unit         \\
		\midrule
		MAC   &  787,969 &  524,800        &    525,313    \\
		S-MAC & 263,168  & 262,656       &    263,168 \\
		\midrule
		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
		\bottomrule
	\end{tabular}
	\label{tab:mac_cell_parameters}
\end{table}

@@

\headerbox{The CLEVR \& CoGenT datasets}{name=datasets, column=1}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
		\caption{\textbf{Q}: \textit{How many objects are either small cylinders or red things?} -- \textbf{A}: 5.}
		\label{fig:clevr_task}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
	  	\compresslist
	  	\item[$\bullet$] The authors~\cite{johnson2017clevr} also introduced CLEVR-CoGenT, to evaluate how well a model can learn relations and compositional concepts.
	  	\item[$\bullet$] Similar to CLEVR, but with two conditions, as follows:
	\end{itemize}
	\vspace{-10pt}
	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT-A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT-B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

@@

\headerbox{Experiments \& Results}{name=experiments, column=1, below=datasets}{
	\vspace{-10pt}
	\begin{table}[H]
	\centering
	\scalebox{1}{
	\begin{tabular}{cccccccc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17 \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

\begin{itemize}
	\compresslist
	\item[$\bullet$] Our experiments on \emph{zero-shot learning} (CoGenT-A $\rightarrow$ CoGenT-B) show that both models have poor performance, in line with
	the other models in the literature.
	\item[$\bullet$] With fine-tuning, both MAC models match state-of-the-art accuracy (a 15pts increase).
	\item[$\bullet$] \textbf{S-MAC presents a 10\% speed-up in training time and comparable accuracy.}
	\item[$\bullet$] Finetuning CLEVR-trained models on CoGenT-A or -B hurts their generalization capabilities.
	\item[$\rightarrow$] \emph{Zero-shot learning} remains an interesting problem to solve.
\end{itemize}

@@

\headerbox{Compositional generalization of the MAC model}{name=mac-failures, column=1, below=experiments}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.71\textwidth]{../img/fail_mac_cogent_b_shape.png}
		\caption{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}
		\label{fig:mac_failure}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
		\compresslist
		\item[$\bullet$] Asked about the shape of the leftmost \textbf{gray cylinder}, the model correctly finds it, (cf. \emph{visual attention map}), and refers to it using its color (\emph{attention over the question words}).
		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \textbf{gray cylinders} during training, but saw \textbf{gray cubes}.
		\item[$\rightarrow$] This indicates that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).
	\end{itemize}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Contributions}{name=contributions,column=0,row=0}{
\begin{itemize}
	\compresslist
	\item We introduce a \emph{\textbf{simplified}} variant of the MAC (Memory,  Attention,
	and Composition) model~\cite{hudson2018compositional}, which achieves comparable accuracy while training \emph{\textbf{faster}}.
	\item We evaluate both the original MAC model and the simplified variant on CLEVR \& CoGenT datasets, and show that \emph{\textbf{transfer learning with fine-tuning}} results in a \emph{\textbf{15 point increase}} in accuracy, matching the state of the art.
	\item We also demonstrate that \emph{\textbf{improper}} fine-tuning can \emph{\textbf{reduce a model's accuracy}}.

@@

\headerbox{The MAC model~\cite{hudson2018compositional}}{name=mac-model, column=0, below=contributions}{
\textbf{MAC network}: a recurrent neural network performing sequential reasoning. At each step, it analyzes the question and shifts the attention over the image.
	\vspace{-3pt}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.4\textwidth]{../img/mac_cell.pdf}
		\caption{\textbf{MAC cell} consists of a control unit, a read unit \& a write unit.}
		\label{fig:mac_cell}
	\end{figure}
	\vspace{-20pt}		 
	\begin{itemize}
	\compresslist
		\item \textbf{Control unit} updates the control state $c_i$ \& shifts the attention over question words.
		\item \textbf{Read unit}, guided by $c_i$, extracts information from the image.
		\item \textbf{Write unit} uses this information to update the memory state $m_i$.
	\end{itemize}
}

\headerbox{The Simplified MAC model (S-MAC)}{name=s-mac, column=0, below=mac-model}{

@@

\begin{itemize}
		\compresslist
	    \item Taking the MAC cell equations as a whole, all consecutive linear layers (with no non-linear activation in-between) can be combined into a single linear layer.
		\item We assume that dimension-preserving linear layers are invertible so as to avoid information loss.
		\item[$\Rightarrow$] This allows, with a careful reorganization, to apply a single linear layer to the \textit{knowledge base} (feature map extracted from the image) prior to all the reasoning steps and work with this projection throughout the reasoning steps.
\end{itemize}

@@

\vspace{-15pt}
\begin{table}[H]
	\centering
	\caption{Comparison of numbers of position-independent parameters between MAC \& S-MAC cells.}
	\begin{tabular}{llll}
		\toprule
		Model        & Read Unit               & Write Unit &  Control Unit         \\
		\midrule
		MAC   &  787,969 &  524,800        &    525,313    \\
		S-MAC & 263,168  & 262,656       &    263,168 \\
		\midrule
		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
		\bottomrule
	\end{tabular}
	\label{tab:mac_cell_parameters}
\end{table}

@@

\headerbox{The CLEVR \& CoGenT datasets}{name=datasets, column=1}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
		\caption{\textbf{Q}: \textit{How many objects are either small cylinders or red things?} \textbf{A}: 5.}
		\label{fig:clevr_task}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
	  	\compresslist
	  	\item The authors of CLEVR~\cite{johnson2017clevr} also introduced a variant called CLEVR-CoGenT, aiming at evaluation of how well models can learn compositional concepts.
	  	\item Similar to CLEVR, but with two conditions, as follows:
	\end{itemize}
	\vspace{-10pt}
	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT-A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT-B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

@@

\headerbox{Experiments \& results}{name=experiments, column=1, below=datasets}{
	\vspace{-10pt}
	\begin{table}[H]
	\centering
	\scalebox{1}{
	\begin{tabular}{cccccccc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17 \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

\begin{itemize}
	\compresslist
	\item Our experiments on \emph{zero-shot learning} (CoGenT-A $\rightarrow$ CoGenT-B) show that both models have poor performance, in line with
	the other models in the literature.
	\item With fine-tuning, both MAC models match state-of-the-art accuracy (a 15pts increase).
	\item \textbf{S-MAC presents a 10\% speed-up in training time and comparable accuracy.}
	\item Finetuning CLEVR-trained models on CoGenT-A or -B hurts their generalization capabilities.
	\item[$\Rightarrow$] \emph{Zero-shot learning} remains an interesting problem to solve.
\end{itemize}

@@

\headerbox{Compositional generalization of the MAC model}{name=mac-failures, column=1, below=experiments}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.71\textwidth]{../img/fail_mac_cogent_b_shape.png}
		\caption{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}
		\label{fig:mac_failure}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
		\compresslist
		\item Asked about the shape of the leftmost \textbf{gray cylinder}, the model correctly finds it, (cf. \emph{visual attention map}), and refers to it using its color (\emph{attention over the question words}).
		\item As it never saw \textbf{gray cylinders} during training, whereas learned the \textbf{gray cubes} compositional concept, the model predicts the shape as a \textbf{cube}.
		\item[$\Rightarrow$] This indicates that MAC does not separate shape from color, but has a better understanding of color cues (as it found the object by its color).
	\end{itemize}
}

### 2019-10-21 MAC_publications/arxiv/smac.tex
Move MAC publications files into subdir

@@

\vskip -1.0cm
\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
	           & \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	{\color{Plum}
	\begin{align*}
	&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
	&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} \rr_i + b_{rm}^{[d]} \tag{w1}
	\end{align*}}
\end{multicols}

>>>>

\noindent\textit{Notation.}
%Let $q$ denote the global context of the question
%and let $\cw_s$ denote the contextual embedding of a word $s$ in the question.
For each knowledge base $\kb$ of dimension $H \times W \times d$, let $\kb_{hw}$ be the $d$-dimensional vector indexed by 
$h \in \{1,2,\dots,H\}$ and $w \in \{1,2,\dots, W\}$.
Let $i$ denote the index of the reasoning steps.

@@

\vskip -0.6cm
\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
	           & \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times 2d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	{\color{Plum}
	\begin{align*}
	&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
	&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} \rr_i + b_{rm}^{[d]} \tag{w1}
	\end{align*}}
\end{multicols}
